Causal Inference in Population Trends: Searching for Demographic Anomalies in Big Data

### 2020-01-28 MANUSCRIPT/manuscript.Rmd
Newest edits. Full paper.
I made the example figure in excel because it was faster.

abstract: "The proliferation of big data, wider access to advanced computing platforms, and the development of powerful statistical algorithms can uncover hidden anomalies in demographic data that have previously been dismissed as noise. Here, we demonstrate how demographers can use causal inference techniques and abductive reasoning to identify fertility and mortality anamolies in state-level data trends by investigating demographic time series data since 1999. In demonstrating our technique, we uncover real spikes and dips in fertility and mortality over time, distinguished from regular trend variations. We show that 36 states exhibited at least one mortality anomaly over time, totalling nearly 300,000 additional deaths, while an additional seven states exhibited periods of decline resuling in 250,000 fewer deaths. Ten states exhibited real, marked periods of declines in fertility, totalling more than 214,000 fewer births than expected, and 8 states had periods of excess births, resulting in an addition 12,000 births. Our results show how researchers can detect demographic anomalies in trend data and use those anomalies as a beginning point for further investigation into the causes."

@@

Causal inference, in its most common usage, is an attempt to uncover the underlying mechanism that results in changes in a phenomenon and have a long history approaches in social sciences [@grimmer2015ppsp]. Often, the identification of a casual mechanism requires either a randomized control trial (RCT) or expert knowledge applied to a natural experiment. For population-level analysis, expensive RCTs usually preclude their widespread adoption [@west2008ajph]. Using natural experiments provide less certainty about causation and fewer opportunities to replicate work but they provide important and widespread insights such as the determinants of migration, however, provides important and more widespread insights on the determinants of migration after Hurricane Katrina in 2006 [@fussellRecoveryMigrationCity2014;@horiDisplacementDynamicsSouthern2009], mini baby booms after electrical blackouts [@fetzer2018jpe], and the highly publicized estimates of excess mortality after Hurricane Maria in Puerto Rico in 2016 [@kishore2018mortality;@santos2018use]. Both RCTs and natural experiments follow traditional, hypothesis testing, inductive scientific paradigms where a question is first posed and scientists generate or find data to answer the question. Such approaches, while extensively utilized and time-tested, are likely to miss important phenomena that might go unnoticed.

@@

In this paper, we use modern statistical outlier detection algorithms [@chen1993joint] on nearly twenty years of mortality and fertility data at the US state-level to identify anomalous demographic behavior. In essence, we identify *effects without knowledge of the cause*. We ask two questions regarding demographic anomalies: What are the hidden baby booms/busts and mortality spikes/dips in the United States over the last twenty years? We do not necessarily know the causes of these anomalies but identifying them allows scientists with more detailed knowledge of local population dynamics, state-level policy making, or macro-economics to explain these phenomena post-hoc. From explanations of phenomena that may have previously gone unnoticed, demographers may be able to better forecast populations and provide policy solutions for impending problems.

@@

where $\pi(B)=\sum_{i=o}^{inf} \pi_iB^i$. The identification of outliers then involves a three step process to (1) identify all potential outliers, $t_j$ and $L_j (B)$, (2) joint estimates of model parameters and outlier effects are computed to identify potentially spurious outliers, and (3) the outliers and effects are re-estimated without spurious outliers. Of importance here is step 2, which relies on some critical value above which an outlier at time point m is considered spurious. Based on Chen and Liu’s [-@chen1993joint] recommendation, we set a critical value of 3.5 which generally minimizes the possibility of Type I errors or false positive outliers.

@@

@@

sums2 <- sums %>%
  dplyr::select(percent_anom = `\\% of Total`, everything())
kable(sums,
       "latex",
       booktabs = T,
       format.args = list(big.mark = ","),
       escape = FALSE,
       caption = "\\textbf{Summary by Demographic Component.}  refers to the number of anomolies for each type and demographic component, States refers to the number of unique states exhibiting that specific Type-demographic component. \\label{sumtable}") %>%
   kable_styling(position = "center")

@@

**\autoref{sumtable}** report the overall number of anomalies we detect of each type for births and deaths and some summary statistics across all anomaly types and **\autoref{fig:summap}** maps these results.
We find considerably more mortality anomalies (n = `r paste(sums[2,2])`) than fertility anomalies (n = `r paste(sums[1,2])`). Given that anomalies are always the product of events [@song2018anomaly], finding more mortality than fertility anomalies is not surprising.  Mortality is likely to spike in response to a catastrophic event (like an earthquake or terrorist attack) or due to a disease outbreak while the effects of a catastrophic event on fertility is less predictable.  One reason for this is that fertility is linked to human decision-making more directly than mortality [@stein2014couples] which results in more varied outcomes, so, for example, researchers find that catastrophic weather events can increase childbearing among those who already have a child, but not among the childless [@Evans2008Hurricanebirth]. Some events, like the 1995 Oklahoma City bombings, resulted in both fertility and mortality changes.  However, changes in fertility manifest over a longer time horizon after an event, and the relationship between a fertility-inducing event and behavior change is less strong than the relationship between a mortality-inducing event (such as a terrorist incident) and death [@Rodgers2005OKBombing]. Of course, not all events that impact fertility and mortality are catastrophic. Researchers have documented that more commonplace events such as massive layoff [@Venkataramani2019] or policy changes [@Livingston2017Cannabis] can also create anomalies in mortality patterns, but we have not found such evidence for fertility.

Consistent with more anomalies across the time series, we find more anomalous deaths (`r paste(prettyNum(sums[2,6], digits = 0, big.mark = ","))`) than anomalous births (`r paste(prettyNum(sums[1,6], digits = 0, big.mark = ","))`). Fertility anomalies overwhelmingly tend toward lower fertility, with only a few fertility anomalies yielding more births. This is consistent with research findings that link high severity weather events to significantly lower fertility [@Evans2008Hurricanebirth]. Conversely, mortality anomalies tend to be more evenly split between positive and negative anomalies, but tend toward more deaths rather than less deaths. Again, this is not surprising, as the kinds of events that increase death (e.g., plant closings are associated with increased opioid death [@Venkataramani2019]) are more common than the events that decrease death (e.g., cannabis legalization is associated with decreased opioid deaths [@Livingston2017Cannabis]). These anomalous deaths and births account for `r sums2$percent_anom[2]`% and `r sums2$percent_anom[1]`% over the entire time series, respectively.

@@

## Mortality 
Since the purpose of our paper is to demonstrate how demographers can make use of causal inference technique, we will not discuss all of our findings here, in this paper.  Instead, we will use a few cases for illustration.  For mortality, we will use New York State as an example (**\autoref{fig:mortnewhamp}a**). We identify seven anomalies in the mortality time series for New York, all with *t*-statistics in excess of 3.91, making these anomalies unlikely to be due to chance. The algorithm correctly identifies September 2001 as an additive outlier (2001:09 *t*= `r paste(prettyNum(outlier.mort.ny$outliers[2,5], digits = 4))`) where there were `r paste(prettyNum(outlier.mort.ny$outliers$coefhat[2], digits = 4, big.mark = ","))` more deaths in that month than anticipated. This mortality event is likely caused by the September 11 tragedy and the detection of this mortality event provides confidence in our detection of other anomalies.

@@

In **\autoref{fig:mortnewhamp}a**, notice the strong level shift (LS) that occurs in February 2004 (2004:02 *t*= `r paste(ny_tstat)`) which prevented `r paste(ny_averteddeaths)` deaths per month. This shift totals more than `r paste(ny_averteddeathstot)` averted deaths compared to the counter-factual time series and is the single largest mortality protective anomaly among all states. This translates to `r ny_peraverted` fewer deaths than expected over the time period. What is driving this mortality protection? What policies did NY put into place that might have contributed to this considerable mortality reduction? What environmental conditions may have changed? These are the kinds of questions that arise from our analyses. The purpose of our paper is not to answer these questions, but our findings underscore the need for more research that takes an abductive approach. By identifying anomalies through an inductive process, researchers can then look for underlying causes. Once those causes are identified, researchers can then use a deductive process to see if such events predict other (or future) anomalies.

@@

conn_tstat <- prettyNum(outlier.fert.conn$outliers$tstat, digits = 3)
conn_births <- prettyNum(outlier.fert.conn$outliers$coefhat, digits = 0)
conn_tot <- prettyNum(sum(outlier.fert.conn$y - outlier.fert.conn$yadj), digits = 0, big.mark = ",")
conn_per <- percent(abs(sum(outlier.fert.conn$y - outlier.fert.conn$yadj) / sum(outlier.fert.conn$yadj[80:180])))
```

To illustrate how researchers can examine fertility anomalies, we begin with a clear temporary change (TC) outlier for fertility in Louisiana (**\autoref{fig:fertla}a**). Here we detect two TC outliers, nearly back-to-back in 2005 (2005:08 *t* = `r la_tstat1`; and 2005:10 *t* = `r la_tstat2`), coinciding with the destruction of Hurricane Katrina from the same year. The migration associated with Hurricane Katrina has garnered most of the attention of demographers [@fussellRecoveryMigrationCity2014;@horiDisplacementDynamicsSouthern2009], but the hurricane had a very clear impact on fertility behaviors too, creating a mini "baby bust" in Louisiana with the departure of many people in their childbearing years. We estimate `r la_averbirths` fewer births in Louisiana compared to the counterfactual, likely attributable to the Hurricane.

We also highlight a level shift (LS) outlier for fertility in Connecticut. Here we detect a strong (*t*= `r conn_tstat` for `r conn_births` births/month) level shift toward lower fertility beginning in August 2009 (2009:08) that continues through the end of the period (**\autoref{fig:fertla}b**). This LS toward lower fertility reduced the # of births by `r conn_tot` or `r conn_per`) lower than the counterfactual time series. The stock market crash of 2008, where the Dow Jones Industrial Average had the largest single-day loss up to that point, occurred just 11 months before we detect a shift toward lower fertility. It is possible that the trend toward lower fertility in August 2009 and the stock market crash in September 2008 are linked, although, as stated previously, we are speculating only to illustrate how causal inference could work in an abductive research agenda.

@@

## Interesting Anomalous Fertility/Mortality events
In the examples above, we highlighted four fertility/mortality anomalies with plausible explanations. In the case of New York and New Hampshire, the mortality anomalies have plausible explanations. It seems likely that New York’s AO anomaly in September 2001 is caused by the 9/11 tragedy and the rise in New Hampshire’s mortality starting in 2010 could be linked to the opioid epidemic. Similarly, Louisiana's TC anomalies seem linked to Hurricanes Katrina and Rita while the LS anomaly in Connecticut's fertility appears linked to the Great Recession. However, we detect numerous seemingly unexplainable demographic anomalies in other states. **\autoref{fig:ferthawaii}** shows two such unexplained anomalies.

```{r, include = FALSE}
hi_tstat <- prettyNum(outlier.fert.hi$outliers$tstat, digits = 3)
hi_per <- percent(1- outlier.fert.hi$y[137]/outlier.fert.hi$yadj[137])

>>>>

abstract: "The proliferation of big data, wider access to advanced computing platforms, and the development of powerful statistical algorithms can uncover hidden anomalies in demographic data that have previously been dismissed as noise. Here, we demonstrate how social scientists can use causal inference techniques and abductive reasoning to identify fertility and mortality anamolies in state-level data trends by investigating demographic time series data since 1999. In demonstrating our technique, we uncover real spikes and dips in fertility and mortality over time, distinguished from regular trend variations. We show that 36 states exhibited at least one mortality anomaly over time, totalling nearly 300,000 additional deaths, while an additional seven states exhibited periods of decline resuling in 250,000 fewer deaths. Ten states exhibited real, marked periods of declines in fertility, totalling more than 214,000 fewer births than expected, and 8 states had periods of excess births, resulting in an addition 12,000 births. Our results show how researchers can detect demographic anomalies in trend data and use those anomalies as a beginning point for further investigation into the causes."

@@

Causal inference, in its most common usage, is an attempt to uncover the underlying mechanisms that result in changes in a phenomenon and has a long history as an approach to inquiry in the social sciences [@grimmer2015ppsp]. Often, the identification of a casual mechanism requires either a randomized control trial (RCT) or expert knowledge applied to a natural experiment. For population-level analysis, expensive RCTs usually preclude their widespread adoption [@west2008ajph]. Using natural experiments provide less certainty about causation and fewer opportunities to replicate work but they provide important and widespread insights.

<!-- such as the determinants of migration, however, provides important and more widespread insights on the determinants of migration after Hurricane Katrina in 2006 [@fussellRecoveryMigrationCity2014;@horiDisplacementDynamicsSouthern2009], mini baby booms after electrical blackouts [@fetzer2018jpe], and the highly publicized estimates of excess mortality after Hurricane Maria in Puerto Rico in 2016 [@kishore2018mortality;@santos2018use]. -->

@@

In this paper, we use modern statistical outlier detection algorithms [@chen1993joint] as a means to illustrate one way that social scientists can engage in discovery using big data techniques on nearly twenty years of mortality and fertility data at the US state-level to identify anomalous demographic behavior. In essence, we identify *effects without knowledge of the cause*. We ask two questions regarding demographic anomalies: What are the hidden baby booms/busts and mortality spikes/dips in the United States over the last twenty years? We do not necessarily know the causes of these anomalies but identifying them allows scientists with more detailed knowledge of local population dynamics, state-level policy making, or macro-economics to explain these phenomena post-hoc. From explanations of phenomena that may have previously gone unnoticed, social scientists may be able to better forecast populations and provide policy solutions for impending problems such as climate change.

@@

![**"Toy" example of anomaly detection using the exchange rate between the Euro and the Swiss Franc.** The Swiss Franc was pegged to the Euro at 1.2 until January 15 2015 when the peg was removed and the currency was allowed to trade more freely. This is a very strong anomly in the time series (*t*-stat = -144.07) detectable using statistical methods and visually. The countefactural estimate with the outlier removed would simply have kept the currency exchange at 1.2 ($\hat{y}$). \label{explanationfigure}](./manuscript_files/figure-latex/Figure1.png)

where $\pi(B)=\sum_{i=o}^{inf} \pi_iB^i$. The identification of outliers then involves a three step process. First, (1) the algorithm identifies all potential outliers, $t_j$ and $L_j (B)$. Next, (2) we compute joint estimates of model parameters and outlier effects to identify potentially spurious outliers. Finally, (3) the outliers and effects are re-estimated without spurious outliers. Of importance here is step 2, which relies on some critical value above which an outlier at time point $m$ is considered spurious. Based on Chen and Liu’s [-@chen1993joint] recommendation, we set a critical value of 3.5 which generally minimizes the possibility of Type I errors or false positive outliers.

```{r, include = FALSE }
set.seed(1)

stockdat <- tribble(
  ~Date, ~Value,
'2014-12-27',	1.203880343,
'2014-12-28',	1.202523908,
'2014-12-29',	1.202714098,
'2014-12-30',	1.201988512,
'2014-12-31',	1.202535102,
'2015-01-01',	1.201727726,
'2015-01-02',	1.201794127,
'2015-01-04',	1.20132752,
'2015-01-05',	1.20100032,
'2015-01-06',	1.20071649,
'2015-01-07',	1.200762136,
'2015-01-08',	1.200787933,
'2015-01-09',	1.20079581,
'2015-01-11',	1.200989867,
'2015-01-12',	1.2006267,
'2015-01-13',	1.20058359,
'2015-01-14',	1.200605219,
'2015-01-15',	0.99417984,
'2015-01-16',	0.992258896,
'2015-01-18',	0.992353824,
'2015-01-19',	1.019880601,
'2015-01-20',	1.00940244,
'2015-01-21',	0.999117945,
'2015-01-22',	0.988725725,
'2015-01-23',	0.939377117,
'2015-01-24',	0.987456601,
'2015-01-25',	0.980699544,
'2015-01-26',	1.013809279,
'2015-01-27',	1.02203072,
'2015-01-28',	1.0234588,
'2015-01-29',	1.0455615
)
dat3 <- ts(stockdat$Value)
stockdat_outlier <- tsoutliers::tso(dat3,types = c("AO","LS","TC"),cval = sigma, maxit.iloop=10)
```

@@

**\autoref{explanationfigure}** shows a toy example for anomaly detection in a time series using the classic example of the exchange rate between the Euro and the Swiss Franc (CHF). On January 15 2015, the Swiss National Bank removed the currency peg of 1.20 francs per Euro, exposing the Franc to the volatility of the currency market. The Franc immediately began trading a reduced rate compared to the Euro. What would have been the Euro/CHF exchange rate had the Swiss National Bank *not* removed the peg? A simple counter-factual estimate would be to keep the exchange rate at 1.20 ($\hat{y}$, sometimes called a "synthetic control" [@abadie2010synthetic]).

In the Swiss Franc example, we have knowledge of the Swiss Bank's activities after the fact or ex-post-facto to to create the counter-factual time series $\hat{y}$ of 1.20. But is this anomaly detectable without knowledge of the Swiss Bank's activities? In other words, can we detect the reduction of the exchange rate on January 15 using only the time series? Absolutely. the tsoutliers package identifies January 15 2015 as an extremely strong level-shift outlier (*t*-stat = `r round( stockdat_outlier$outliers$tstat[1], digits = 2)`). The real world is hardly this simplified where a direct intervention is known and is testable.

@@

sums2 <- sums %>%
  dplyr::select(percent_anom = `\\% of Total`, everything())
kable(sums,
       "latex",
       booktabs = T,
       format.args = list(big.mark = ","),
       escape = FALSE,
       caption = "\\textbf{Summary by Demographic Component.}  Here we can see there 22 Fertility and 156 Mortality anomalies among the state-level time series, totalling more than 200k anomalous births and 600k anomalous deaths. \\label{sumtable}") %>%
   kable_styling(position = "center")

@@

**\autoref{sumtable}** reports the overall number of anomalies we detect of each type for births and deaths and some summary statistics across all anomaly types and **\autoref{fig:summap}** maps these results.
We find considerably more mortality anomalies (n = `r paste(sums[2,2])`) than fertility anomalies (n = `r paste(sums[1,2])`). Given that anomalies are always the product of events [@song2018anomaly], finding more mortality than fertility anomalies is not surprising.  Mortality is likely to spike in response to a catastrophic event (like an earthquake or terrorist attack) or due to a disease outbreak while the effects of a catastrophic event on fertility is less predictable.  One reason for this is that fertility is linked to human decision-making more directly than mortality [@stein2014couples] which results in more varied outcomes, so, for example, researchers find that catastrophic weather events can increase childbearing among those who already have a child, but not among the childless [@Evans2008Hurricanebirth]. Some events, like the 1995 Oklahoma City bombings, resulted in both fertility and mortality changes.  However, changes in fertility manifest over a longer time horizon after an event, and the relationship between a fertility-inducing event and behavior change is less strong than the relationship between a mortality-inducing event (such as a terrorist incident) and death [@Rodgers2005OKBombing]. Of course, not all events that impact fertility and mortality are catastrophic. Researchers have documented that more commonplace events such as massive layoffs [@Venkataramani2019] or policy changes [@Livingston2017Cannabis] can also create anomalies in mortality patterns, but we have not found such evidence for fertility.

Consistent with more anomalies across the time series, we find more anomalous deaths (`r paste(prettyNum(sums[2,6], digits = 0, big.mark = ","))`) than anomalous births (`r paste(prettyNum(sums[1,6], digits = 0, big.mark = ","))`). Fertility anomalies overwhelmingly tend toward lower fertility, with only a few fertility anomalies yielding more births. This is consistent with research findings that link high severity weather events to significantly lower fertility [@Evans2008Hurricanebirth]. Conversely, mortality anomalies tend to be more evenly split between positive and negative anomalies, but tend toward more deaths rather than fewer deaths. Again, this is not surprising, as the kinds of events that increase death (e.g., plant closings are associated with increased opioid death [@Venkataramani2019]) are more common than the events that decrease death (e.g., cannabis legalization is associated with decreased opioid deaths [@Livingston2017Cannabis]). These anomalous deaths and births account for `r sums2$percent_anom[2]`% and `r sums2$percent_anom[1]`% over the entire time series, respectively.

@@

## Mortality 
Since the purpose of our paper is to demonstrate how social scientists can make use of causal inference technique, we will not discuss all of our findings in this paper.  Instead, we will use a few cases for illustration.  For mortality, we will use New York State as an example (**\autoref{fig:mortnewhamp}a**). We identify seven anomalies in the mortality time series for New York, all with *t*-statistics in excess of 3.91, making these anomalies unlikely to be due to chance. The algorithm correctly identifies September 2001 as an additive outlier (2001:09 *t*= `r paste(prettyNum(outlier.mort.ny$outliers[2,5], digits = 4))`) where there were `r paste(prettyNum(outlier.mort.ny$outliers$coefhat[2], digits = 4, big.mark = ","))` more deaths in that month than anticipated. This mortality event is likely caused by the September 11 terrorist attack on the World Trade Center that immediately killed 2,606 people and the detection of this mortality event provides confidence in our detection of other anomalies.

@@

In **\autoref{fig:mortnewhamp}a**, notice the strong level shift (LS) that occurs in February 2004 (2004:02 *t*= `r paste(ny_tstat)`) which prevented `r paste(ny_averteddeaths)` deaths per month. This shift totals more than `r paste(ny_averteddeathstot)` averted deaths compared to the counter-factual time series and is the single largest mortality protective anomaly among all states. This translates to `r ny_peraverted` fewer deaths than expected over the time period. What is driving this mortality protection? What policies did NY put into place that might have contributed to this considerable mortality reduction? What environmental or economic conditions may have changed may have changed? These are the kinds of questions that arise from our analyses. The purpose of our paper is not to answer these questions, but our findings underscore the need for more research that takes an abductive approach. By identifying anomalies through an inductive process, researchers can then look for underlying causes. Once those causes are identified, researchers can then use a deductive process to see if such events predict other (or future) anomalies.

@@

conn_tstat <- prettyNum(outlier.fert.conn$outliers$tstat, digits = 3)
conn_births <- prettyNum(outlier.fert.conn$outliers$coefhat, digits = 0)
conn_tot <- prettyNum(abs(sum(outlier.fert.conn$y - outlier.fert.conn$yadj)), digits = 0, big.mark = ",")
conn_per <- percent(abs(sum(outlier.fert.conn$y - outlier.fert.conn$yadj) / sum(outlier.fert.conn$yadj[80:180])))
```

To illustrate how researchers can examine fertility anomalies, we begin with a clear temporary change (TC) outlier for fertility in Louisiana (**\autoref{fig:fertla}a**). Here we detect two TC outliers, nearly back-to-back in 2005 (2005:08 *t* = `r la_tstat1`; and 2005:10 *t* = `r la_tstat2`), coinciding with the destruction of Hurricane Katrina from the same year. The migration associated with Hurricane Katrina has garnered most of the attention of social scientists [@fussellRecoveryMigrationCity2014;@horiDisplacementDynamicsSouthern2009], but the hurricane had a very clear impact on fertility behaviors too, creating a mini "baby bust" in Louisiana with the departure of many people in their childbearing years. We estimate `r la_averbirths` fewer births in Louisiana compared to the counterfactual, likely attributable to the Hurricane.

We also highlight a level shift (LS) outlier for fertility in Connecticut. Here we detect a strong (*t*= `r conn_tstat` for `r conn_births` births/month) level shift toward lower fertility beginning in August 2009 (2009:08) that continues through the end of the period (**\autoref{fig:fertla}b**). This LS toward lower fertility reduced the number of births by `r conn_tot` or `r conn_per`) lower than the counterfactual time series. The stock market crash of 2008, where the Dow Jones Industrial Average had the largest single-day loss up to that point, occurred just 11 months before we detect a shift toward lower fertility. It is possible that the trend toward lower fertility in August 2009 and the stock market crash in September 2008 are linked, although, as stated previously, we are speculating only to illustrate how causal inference could work in an abductive research agenda. A potentially interesting future line of research would be to link fertility anomalies to the kinds of economic shocks that may lead to outmigration of those in their childbearing years.

@@

## Interesting Anomalous Fertility/Mortality events
In the examples above, we highlighted four fertility/mortality anomalies with plausible explanations. In the case of New York and New Hampshire, the mortality anomalies have plausible explanations. It seems likely that New York’s AO anomaly in September 2001 is caused by the 9/11 tragedy and the rise in New Hampshire’s mortality starting in 2010 could be linked to the opioid epidemic. Similarly, Louisiana's TC anomalies seem linked to Hurricanes Katrina and Rita while the LS anomaly in Connecticut's fertility appears linked to the Great Recession. However, we detect numerous other demographic anomalies in other states, on the causes of which we will not speculate. **\autoref{fig:ferthawaii}** shows two such unexplained anomalies.

```{r, include = FALSE}
hi_tstat <- prettyNum(outlier.fert.hi$outliers$tstat, digits = 3)
hi_per <- percent(abs(1- outlier.fert.hi$y[137]/outlier.fert.hi$yadj[137]))
